---
title: "Statistical analysis on AP-1 transcription factor"
author: "Yuyang Yuan, Shuhan Sun, Mingyu Zhang, Frank Li"
subtitle: "STA130 Poster Project"
date: December 6, 2022
output: 
  beamer_presentation:
    theme: "Pittsburgh"
    colortheme: "orchid"
    fonttheme: "structurebold"
    slide_level: 2
classoption: "aspectratio=169"
fontsize: 11pt
urlcolor: blue
---


```{r, include=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
library(corrplot)
library(psych)
Project_data <- read_csv("STA130_Course_Project.csv")
glimpse(Project_data)
```


## Introduction

Background information:\
  - Cancer has long been a devastating disease that torturing thousand millions of people\
  - Vast of experiments and clinical trials have been made around the cancer treatment\
  - Researchers have found that melanoma cells are typically resistant to commonly used MAPK inhibitors\
  - AP-1 transcription factor can cause melanoma cells to change their status\

This projects aims to study the relationships between different AP-1 transcription factor and or other factors in different condition based the data provided.

## Objectives
### This project will answer the three following questions (x and t will be specified later):
  1. Do protein levels in experimental condition x change over time t?\
  2. At time t in experimental condition x, what is the relationship between different proteins?\
  3. At time 24h in experimental condition drug_id == 1 & dose_id == 1 & Rep == 1m, which the AP-1 protein can predict the MITF protein?


## Data Summary

Raw data used in this project includes 26 variables in total, in which 22 of them are AP-1 transcription factors and 4 are phenotype proteins.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
head(Project_data)
```
- The specific variables and data selected to answer each question will be explained in details later.



## Research question one: Intro to the question

### Research Question one: Do protein levels of Ki_67 in experimental condition x change over time t?

- Method: two samples hypothesis test for mean\
- Why using two samples hypothesis?\
- Aiming to find: whether the protein level for a certain protein changes in \ fixed condition x over two different time point
- Condition x choose: Rep = 1 & drug_id = 1 & dose_id = 2
- time t choose: Timepoint = "0.5 h" and Timepoint = "72 h"\

## Research question one: Data visualization

```{r,include=TRUE, echo=FALSE,fig.width=4, fig.height=1.5}
Project_data_Q1 <- Project_data %>% 
  filter((Timepoint == "0.5 h" | Timepoint == "72 h") & 
           Rep == 1 & drug_id == 1 & dose_id == 2) %>%
  select(Ki_67,Timepoint)
proj_d1 <- Project_data_Q1 %>% filter(Timepoint == "0.5 h")
proj_d1 %>% ggplot(aes(x=Ki_67)) + 
  geom_histogram(bins=10, fill="gray", colour = "black") + labs(x="protein level for Ki_67 at Timepoint = 0.5 h")
proj_d2 <- Project_data_Q1 %>% filter(Timepoint == "72 h")
proj_d2 %>% ggplot(aes(x=Ki_67)) + 
  geom_histogram(bins=10, fill="gray", colour = "black") + labs(x="protein level for Ki_67 at Timepoint = 72 h")

```


## Research question one: Statistical Method

- Method: two samples hypothesis test for mean

Hypothesis:
$$H_0:\mu_{0.5 h} = \mu_{72 h}$$
$$H_A: \mu_{0.5 h} \neq \mu_{72 h}$$

- Where $\mu_{0.5 h}$ is mean of Ki_67 at Timepoint equals 0.5 hours and $\mu_{0.5 h}$ is mean of Ki_67 at Timepoint equals 72 hours.

- `Ki_67` represents the protein level at certain condition and timepoint; `Timepoint` represents the time at which the protein level is measured.

## Research question one: Statistical Method And Results

- Step one: Calculation of test statistics
```{r, echo=FALSE, message=FALSE, warning=FALSE,}
test_stat <- Project_data_Q1 %>% group_by(Timepoint) %>%
summarise(means = mean(Ki_67), .groups="drop") %>%
summarise(value = diff(means))
test_stat <- as.numeric(test_stat)
test_stat
```

- Step two: Data simulation
```{r, echo=FALSE, message=FALSE, warning=FALSE,}
set.seed(999) # any number you like
repetitions <- 1000;
simulated_values <- rep(NA, repetitions)

for(i in 1:repetitions){
  simdata <- Project_data_Q1 %>% mutate(Timepoint= sample(Timepoint))
  sim_value <- simdata %>% group_by(Timepoint) %>%
    summarise(means = mean(Ki_67)) %>%
  summarise(value = diff(means))
  simulated_values[i] <- as.numeric(sim_value)
}

sim <- tibble(mean_diff = simulated_values)
```


- Step three: Calculation of the p-value
```{r, echo=FALSE, message=FALSE, warning=FALSE,}
num_more_extreme <- sim %>% filter(abs(mean_diff) >= abs(test_stat)) %>% 
  summarise(n())
p_value <- as.numeric(num_more_extreme / repetitions)
print(p_value)
```

- The p-value shows the probability of obtaining test results at least as extreme as
the result actually observed. In this case, for significance level alpha to be 0.05,
since p-value < 0.05, we have enough evidence to reject the null hypothesis.
- Conclusion: protein level of Ki_67 changes with time


## Research question one: Further Examination

- The conclusion that we made in the last page is only responsible for the specific
condition and time period
- We would like to perform some more comparison to strengthen our believe with it
- We will include changes in: 
  - doses  
  - drug used
  - repetitions
- We would also like to include both change of protein level in both short term (0.5 hours
to 2 hours) and long term (0.5 hours to 72 hours)

## Research question one: Further Examination

- Original Condition: Rep = 1 & drug_id = 1 (Drug = Vem) & dose_id = 2 (Doses = 0.1uM)
  - Short term: test statistics: -0.01442442, p-value = 0.039
```{r, include=FALSE, echo=TRUE, message=FALSE, warning=FALSE,}
Project_data_Q1 <- Project_data %>% 
  filter((Timepoint == "0.5 h" | Timepoint == "2 h") & 
           Rep == 1 & drug_id == 1 & dose_id == 2) %>%
  select(Ki_67,Timepoint)
proj_d1 <- Project_data_Q1 %>% filter(Timepoint == "0.5 h")
proj_d2 <- Project_data_Q1 %>% filter(Timepoint == "2 h")

test_stat <- Project_data_Q1 %>% group_by(Timepoint) %>%
summarise(means = mean(Ki_67), .groups="drop") %>%
summarise(value = diff(means))
test_stat <- as.numeric(test_stat)

set.seed(999) # any number you like
repetitions <- 1000;
simulated_values <- rep(NA, repetitions)

for(i in 1:repetitions){
  simdata <- Project_data_Q1 %>% mutate(Timepoint= sample(Timepoint))
  sim_value <- simdata %>% group_by(Timepoint) %>%
    summarise(means = mean(Ki_67)) %>%
  summarise(value = diff(means))
  simulated_values[i] <- as.numeric(sim_value)
}

sim <- tibble(mean_diff = simulated_values)

num_more_extreme <- sim %>% filter(abs(mean_diff) >= abs(test_stat)) %>% 
  summarise(n())
p_value <- as.numeric(num_more_extreme / repetitions)
```
  - Long term: test statistics:  -0.5309462, p-value = 0
  
- More repetitions: Rep = 2 & drug_id = 1 (Drug = Vem) & dose_id = 2 (Doses = 0.1uM)
  - Short term: test statistics: -0.004843381, p-value = 0.487
```{r, include=FALSE, echo=TRUE, message=FALSE, warning=FALSE,}
Project_data_Q1 <- Project_data %>% 
  filter((Timepoint == "0.5 h" | Timepoint == "2 h") & 
           Rep == 2 & drug_id == 1 & dose_id == 2) %>%
  select(Ki_67,Timepoint)
proj_d1 <- Project_data_Q1 %>% filter(Timepoint == "0.5 h")
proj_d2 <- Project_data_Q1 %>% filter(Timepoint == "2 h")

test_stat <- Project_data_Q1 %>% group_by(Timepoint) %>%
summarise(means = mean(Ki_67), .groups="drop") %>%
summarise(value = diff(means))
test_stat <- as.numeric(test_stat)
test_stat

set.seed(999) # any number you like
repetitions <- 1000;
simulated_values <- rep(NA, repetitions)

for(i in 1:repetitions){
  simdata <- Project_data_Q1 %>% mutate(Timepoint= sample(Timepoint))
  sim_value <- simdata %>% group_by(Timepoint) %>%
    summarise(means = mean(Ki_67)) %>%
  summarise(value = diff(means))
  simulated_values[i] <- as.numeric(sim_value)
}

sim <- tibble(mean_diff = simulated_values)

num_more_extreme <- sim %>% filter(abs(mean_diff) >= abs(test_stat)) %>% 
  summarise(n())
p_value <- as.numeric(num_more_extreme / repetitions)
p_value
```
  - Long term: test statistics:  -0.5346298, p-value = 0
```{r, include=FALSE, echo=TRUE, message=FALSE, warning=FALSE,}
Project_data_Q1 <- Project_data %>% 
  filter((Timepoint == "0.5 h" | Timepoint == "72 h") & 
           Rep == 2 & drug_id == 1 & dose_id == 2) %>%
  select(Ki_67,Timepoint)
proj_d1 <- Project_data_Q1 %>% filter(Timepoint == "0.5 h")
proj_d2 <- Project_data_Q1 %>% filter(Timepoint == "72 h")

test_stat <- Project_data_Q1 %>% group_by(Timepoint) %>%
summarise(means = mean(Ki_67), .groups="drop") %>%
summarise(value = diff(means))
test_stat <- as.numeric(test_stat)
test_stat

set.seed(999) # any number you like
repetitions <- 1000;
simulated_values <- rep(NA, repetitions)

for(i in 1:repetitions){
  simdata <- Project_data_Q1 %>% mutate(Timepoint= sample(Timepoint))
  sim_value <- simdata %>% group_by(Timepoint) %>%
    summarise(means = mean(Ki_67)) %>%
  summarise(value = diff(means))
  simulated_values[i] <- as.numeric(sim_value)
}

sim <- tibble(mean_diff = simulated_values)

num_more_extreme <- sim %>% filter(abs(mean_diff) >= abs(test_stat)) %>% 
  summarise(n())
p_value <- as.numeric(num_more_extreme / repetitions)
p_value
```

- Two drugs: Rep = 1 & drug_id = 2 (Drug = Vem+Tram) & dose_id = 2 (Doses = 0.1uM)
  - Short term: test statistics: -0.05653635, p-value = 0
```{r, include=FALSE, echo=TRUE, message=FALSE, warning=FALSE,}
Project_data_Q1 <- Project_data %>% 
  filter((Timepoint == "0.5 h" | Timepoint == "2 h") & 
           Rep == 1 & drug_id == 2 & dose_id == 2) %>%
  select(Ki_67,Timepoint)
proj_d1 <- Project_data_Q1 %>% filter(Timepoint == "0.5 h")
proj_d2 <- Project_data_Q1 %>% filter(Timepoint == "2 h")

test_stat <- Project_data_Q1 %>% group_by(Timepoint) %>%
summarise(means = mean(Ki_67), .groups="drop") %>%
summarise(value = diff(means))
test_stat <- as.numeric(test_stat)
test_stat

set.seed(999) # any number you like
repetitions <- 1000;
simulated_values <- rep(NA, repetitions)

for(i in 1:repetitions){
  simdata <- Project_data_Q1 %>% mutate(Timepoint= sample(Timepoint))
  sim_value <- simdata %>% group_by(Timepoint) %>%
    summarise(means = mean(Ki_67)) %>%
  summarise(value = diff(means))
  simulated_values[i] <- as.numeric(sim_value)
}

sim <- tibble(mean_diff = simulated_values)

num_more_extreme <- sim %>% filter(abs(mean_diff) >= abs(test_stat)) %>% 
  summarise(n())
p_value <- as.numeric(num_more_extreme / repetitions)
p_value
```
  - Long term: test statistics:  -0.827778, p-value = 0
```{r, include=FALSE, echo=TRUE, message=FALSE, warning=FALSE,}
Project_data_Q1 <- Project_data %>% 
  filter((Timepoint == "0.5 h" | Timepoint == "72 h") & 
           Rep == 1 & drug_id == 2 & dose_id == 2) %>%
  select(Ki_67,Timepoint)
proj_d1 <- Project_data_Q1 %>% filter(Timepoint == "0.5 h")
proj_d2 <- Project_data_Q1 %>% filter(Timepoint == "72 h")

test_stat <- Project_data_Q1 %>% group_by(Timepoint) %>%
summarise(means = mean(Ki_67), .groups="drop") %>%
summarise(value = diff(means))
test_stat <- as.numeric(test_stat)
test_stat

set.seed(999) # any number you like
repetitions <- 1000;
simulated_values <- rep(NA, repetitions)

for(i in 1:repetitions){
  simdata <- Project_data_Q1 %>% mutate(Timepoint= sample(Timepoint))
  sim_value <- simdata %>% group_by(Timepoint) %>%
    summarise(means = mean(Ki_67)) %>%
  summarise(value = diff(means))
  simulated_values[i] <- as.numeric(sim_value)
}

sim <- tibble(mean_diff = simulated_values)

num_more_extreme <- sim %>% filter(abs(mean_diff) >= abs(test_stat)) %>% 
  summarise(n())
p_value <- as.numeric(num_more_extreme / repetitions)
p_value
```

- Larger Dose: Rep = 1 & drug_id = 1 (Drug = Vem) & dose_id = 3 (Doses = 0.316uM)
  - Short term: test statistics:  -0.02280144, p-value = 0.001
```{r, include=FALSE, echo=TRUE, message=FALSE, warning=FALSE,}
Project_data_Q1 <- Project_data %>% 
  filter((Timepoint == "0.5 h" | Timepoint == "2 h") & 
           Rep == 1 & drug_id == 1 & dose_id == 3) %>%
  select(Ki_67,Timepoint)
proj_d1 <- Project_data_Q1 %>% filter(Timepoint == "0.5 h")
proj_d2 <- Project_data_Q1 %>% filter(Timepoint == "2 h")

test_stat <- Project_data_Q1 %>% group_by(Timepoint) %>%
summarise(means = mean(Ki_67), .groups="drop") %>%
summarise(value = diff(means))
test_stat <- as.numeric(test_stat)
test_stat

set.seed(999) # any number you like
repetitions <- 1000;
simulated_values <- rep(NA, repetitions)

for(i in 1:repetitions){
  simdata <- Project_data_Q1 %>% mutate(Timepoint= sample(Timepoint))
  sim_value <- simdata %>% group_by(Timepoint) %>%
    summarise(means = mean(Ki_67)) %>%
  summarise(value = diff(means))
  simulated_values[i] <- as.numeric(sim_value)
}

sim <- tibble(mean_diff = simulated_values)

num_more_extreme <- sim %>% filter(abs(mean_diff) >= abs(test_stat)) %>% 
  summarise(n())
p_value <- as.numeric(num_more_extreme / repetitions)
p_value
```
  - Long term: test statistics: -0.7973515, p-value = 0
```{r, include=FALSE, echo=TRUE, message=FALSE, warning=FALSE,}
Project_data_Q1 <- Project_data %>% 
  filter((Timepoint == "0.5 h" | Timepoint == "72 h") & 
           Rep == 1 & drug_id == 1 & dose_id == 3) %>%
  select(Ki_67,Timepoint)
proj_d1 <- Project_data_Q1 %>% filter(Timepoint == "0.5 h")
proj_d2 <- Project_data_Q1 %>% filter(Timepoint == "72 h")

test_stat <- Project_data_Q1 %>% group_by(Timepoint) %>%
summarise(means = mean(Ki_67), .groups="drop") %>%
summarise(value = diff(means))
test_stat <- as.numeric(test_stat)
test_stat

set.seed(999) # any number you like
repetitions <- 1000;
simulated_values <- rep(NA, repetitions)

for(i in 1:repetitions){
  simdata <- Project_data_Q1 %>% mutate(Timepoint= sample(Timepoint))
  sim_value <- simdata %>% group_by(Timepoint) %>%
    summarise(means = mean(Ki_67)) %>%
  summarise(value = diff(means))
  simulated_values[i] <- as.numeric(sim_value)
}

sim <- tibble(mean_diff = simulated_values)

num_more_extreme <- sim %>% filter(abs(mean_diff) >= abs(test_stat)) %>% 
  summarise(n())
p_value <- as.numeric(num_more_extreme / repetitions)
p_value
```



## Reasearch question two: intro to the question

### At time 15h in experimental condition drug_id == 1 & dose_id == 1 & Rep == 1,\ what is the relationship between different proteins?

- Method: Correlation Estimation
- The variable that has been chosen for this question are:
  - 'Phospho_ATF1'
  - 'ATF6'
  - 'Fra1'
  - 'NF_kappaB'
- Compute the correlation estimation between the selected variables at the specific defined time and condition


## Reasearch question two: Statistical Method

*Mathematical representation of the method*
$$
r=\frac{\sum_{i=1}^n\left(x_i-\bar{x}\right)\left(y_i-\bar{y}\right)}{\sqrt{\sum_{i=1}^n\left(x_i-\bar{x}\right)^2 \sum_{i=1}^n\left(y_i-\bar{y}\right)^2}}
$$
- calculating the Pearson’s correlation\
- For example, $x_i$ could be variable 'ATF6' and $y_i$ could be variable 'Fra1'

## Reasearch question two: data visualization(p1)
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4}
Project_data %>% 
  ggplot(aes(x=Phospho_ATF1, y=ATF6)) +
  geom_point()+
  geom_smooth(method="lm", se=FALSE)
```

## Reasearch question two: data visualization(p2)
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4}

Project_data %>% 
  ggplot(aes(x=Phospho_ATF1, y=Fra1)) +
  geom_point()+
  geom_smooth(method="lm", se=FALSE)
```

## Reasearch question two: data visualization(p3)
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4}

Project_data %>% 
  ggplot(aes(x=Phospho_ATF1, y=NF_kappaB)) +
  geom_point()+
  geom_smooth(method="lm", se=FALSE)
```

## Reasearch question two: data visualization(p4)
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4}

Project_data %>% 
  ggplot(aes(x=ATF6, y=Fra1)) +
  geom_point()+
  geom_smooth(method="lm", se=FALSE)

```

## Reasearch question two: data visualization(p5)
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4}

Project_data %>% 
  ggplot(aes(x=ATF6, y=NF_kappaB)) +
  geom_point()+
  geom_smooth(method="lm", se=FALSE)

```

## Reasearch question two: data visualization(p6)
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4}

Project_data %>% 
  ggplot(aes(x=Fra1, y=NF_kappaB)) +
  geom_point()+
  geom_smooth(method="lm", se=FALSE)

```



## Reasearch question two: Result

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4, fig.align='center'}
Project_data_Q3 <- Project_data %>% 
  filter(timepoint_id == 5 & 
           drug_id == 1 & 
           dose_id == 1) #or use Timepoint & Drugs & Doses

ATF6_Fra1 <- cor(Project_data_Q3$ATF6, Project_data_Q3$Fra1)
ATF6_NF_kappaB <- cor(Project_data_Q3$ATF6, Project_data_Q3$NF_kappaB)
ATF6_Phospho_ATF1 <- cor(Project_data_Q3$ATF6, Project_data_Q3$Phospho_ATF1)
Fra1_NF_kappaB <- cor(Project_data_Q3$Fra1, Project_data_Q3$NF_kappaB)
Fra1_Phospho_ATF1 <- cor(Project_data_Q3$Fra1, Project_data_Q3$Phospho_ATF1)
NF_kappaB_Phospho_ATF1 <- cor(Project_data_Q3$NF_kappaB, Project_data_Q3$Phospho_ATF1)
library(knitr)
r <- tibble(ATF6_Fra1, ATF6_NF_kappaB)
kable(r)
h <- tibble( ATF6_Phospho_ATF1, Fra1_NF_kappaB )
kable(h)
w <- tibble(Fra1_Phospho_ATF1, NF_kappaB_Phospho_ATF1)
kable(w)
```

## Reasearch question two: Result
- Six pair of correlation: 
  1. ATF6 and Fra1: Positive weak
  2. ATF6 and NF_kappaB: Positive strong
  3. ATF6 and Phospho_ATF1: Positive median
  4. Fra1 and NF_kappaB: Positive weak
  5. Fra1 and Phospho_ATF1: Positive median
  6. NF and kappaB_Phospho_ATF1: Positive median
- All positive, but with different strength
- Suggesting correlation but not causation



## Reasearch question three: intro to the question

### At time 24h in experimental condition drug_id == 1 & dose_id == 1 & Rep == 1, Which AP-1 protein can predict the MITF protein?

- Method: Simple linear regression\
- The variable that has been chosen for this question are\
  - ALL 'AP-1 protein'\
  - 'MITF protein'\
- Analysis the relationship between the selected x variables(AP-1 protein) and y variable(MITF protein) at the specific defined time and condition.


## Reasearch question three: Statistical Method
$$y_i = \beta_0 + \beta_1  x_i+ \epsilon_i$$
- $y_i$ : MITF protein\
- $x_i$ : AP-1 protein\
- $beta_0$ : intercept\
- $beta_1$ : slope\
- $\epsilon$ : random error term\


## Reasearch question three: Data analysis
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4, fig.align='center'}
lr_model <- Project_data %>% filter(drug_id == 1 & dose_id == 1 & Rep == 1 & Timepoint == '24 h')
lr_model <- subset(lr_model, select = -c(...1,NGFR,AXL,Sox10))
set.seed(1399)
n <- nrow(lr_model)
training_indices <- sample(1:n, size = round(0.8*n))
lr_model <- lr_model %>% rowid_to_column()
train <- lr_model %>% filter(rowid %in% training_indices)
test <- lr_model %>% filter(!rowid %in% training_indices)
y_train <- train$MiTFg
y_test <- test$MiTFg
fitted_model <- lm(MiTFg ~ Phospho_c_Fos + Phospho_Fra1 + c_Fos + c_Jun + Fra1 +JunD + ATF2 + JunB + Fra2 + ATF4 + Phospho_Erk1 + Phospho_ATF1 + ATF6 + Phospho_S6 + ATF3 + ATF5 + Phospho_p38 + Ki_67 + Phospho_ATF2 + Phospho_ATF4 + Phospho_c_Jun + NF_kappaB, data = train)
summary(fitted_model)
```


## Reasearch question three: Data analysis
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4, fig.align='center'}
fitted_model_updated <- lm(MiTFg ~ Phospho_c_Fos + Phospho_Fra1 + c_Fos + c_Jun + Fra1 + JunD + JunB + Fra2 + ATF4 + Phospho_Erk1 + Phospho_ATF1 + ATF6 + Phospho_S6 + Phospho_p38 + Ki_67 + NF_kappaB, data = train)
summary(fitted_model_updated)
```


## Reasearch question three: Result
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4, fig.align='center'}
model_test <- predict(fitted_model_updated, newdata = test)
test_RMSE <- sqrt(mean((y_test - model_test)^2))
model_train <- predict(fitted_model_updated, newdata = train)
train_RMSE <- sqrt(mean((y_train - model_train)^2))
c(test_RMSE, train_RMSE)
```
- Meaning of the result, root mean square are similar between train and test group. So the AP-1 protein list in the "fitted_model_updated" can do a good predict to the MITF protein.


## Overall Conclusion

- Q1: Protein level of Ki_67 changes with time in most cases\
    - Example: When Rep == 1, drug_id = 1, dose_id = 2, with time from 0.5hours to 72 hours, test statistics = -0.5309462, p-value = 0\
    - Reject Null hypothesis in this case\

- Q2: The correlation between the four variables (6 paires) at the specified condition are all positive but with different strength.
    - ATF6 and Fra1: Positive weak, ATF6 and NF_kappaB: Positive strong, ATF6 and Phospho_ATF1: Positive median\
    - Fra1 and NF_kappaB: Positive weak, Fra1 and Phospho_ATF1: Positive median, NF and kappaB_Phospho_ATF1: Positive median\

- Q3: Root mean square are similar between train and test group. So the AP-1 protein list in the "fitted_model_updated" can do a good predict to the MITF protein.



## References

101, R Programming. R programming in one hour - a crash course for beginners. 27 April 2022. 7 December 2022.


